Structured Payments in Pawnshop Borrowing:\\ Mandates vs. Choice

### 2025-04-25 presentations/PresentationWinsconsin2025.tex
First set of edits after R&R

\date{Sept 2024}

@@

\begin{frame}{Flexibility and high default}
    \begin{itemize}
    \item Pawn loans are highly \textbf{flexible:} pay-when-you-want within 90 days, no structured payments, no reminders.
        \begin{itemize}
            \item This lack of structure contrasts with microfinance loans.
        \end{itemize}
    \vfill \item High default rates, 44\% in our data (an order of magnitude larger than microfinance).
    \begin{itemize}
        \item Subjective value higher than gold value $\Rightarrow$ inefficient to lose.
        \item Gold-buying stores (avg of 2.8) close to pawn shops (pay $\approx$ 100\% of its gold value).
    \end{itemize}
     \item \vfill \textbf{Optimistic borrowers}: In our data, borrowers are very optimistic about recovery: avg. subjective probability of recovery (0-100) in our data is 92\%.
     \begin{itemize}
         \item Conditional on default: more than 2/5 pay towards recovery (avg. 42\% loan value).
     \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Questions}
     \begin{enumerate}
         \item  Could borrowers benefit from \textbf{frequent payments}, but contract not be offered by lenders?
         \item \vfill If such a contract were offered, would it be demanded by borrowers?
        \item \vfill Would \textbf{mandating} frequent payments reduce financing costs more than giving a menu of \textbf{choices}?
        \item \vfill What is the treatment effect of frequent payments on those who would \textbf{not} choose them (TuT)? And, is there selection on gains for those choosing them?
     \end{enumerate}
\end{frame}

\begin{frame}{Outline}
     \large   
     \begin{itemize}
        \item \textbf{Context: Borrowers, contracts, data, outcomes}
         \item \vfill ``Mandates-Choice'' Experimental Design
         \vfill\item Main results
          \vfill\item Exploiting ``Mandates-Choice'' Design: ToT, TuT
         \vfill\item Why low demand
         %\vfill \item Targeting?
     \end{itemize}
\end{frame}

@@

\begin{frame}{Mandates-Choice Design}
\label{treatment_arms}
   \begin{itemize}
    \vfill \item Randomization at the branch-day level.  Analysis at the pawn level.
    \begin{enumerate}
        \vfill \item Status quo contract (Control, 1770 obs)
       \vfill \item Structured payments (Frequent payments, 1954 obs)
       \vfill \item Choice between the two (2580 obs)
    \end{enumerate}
       \vfill \item  This design enables us to explore whether giving choice saves borrowers more money than assigning them to a Structured payment contract.
       \vfill \item The existence of a Choice arm allows us to measure if there is demand for such a contract. Will also allow more cool stuff... 
\end{itemize}
\end{frame}

\begin{frame}{More details on implementation}
    \begin{itemize}
        \item No person knew sequence of days-contract type.
        \item  Personnel were told that consecutive same contract-type could occur, and that randomization was happening in many if not all branches.
        \item We had materials to explain the contract in simple terms.
        \item Borrowers explained back the contract.
        \item Appraisers no incentive either way (paid flat wage). Enumerators were there every day all day.
        \item Virtually no borrower left the branch without pawning.
        \item They seem to like this lender: 87\% pawned there before.
        \item Stick to branch: we cannot find experimental subjects in 2 different experimental branches. 
    \end{itemize}
\end{frame}

\begin{frame}{Status quo contract}
\vspace{-.2in}
    \begin{figure}[H]
    \label{ExplanatoryMaterial1}
    \begin{center}
        \includegraphics[width=0.34\textwidth]{Figuras/sq_contract.png}
    \end{center}
\end{figure}
\end{frame}

\begin{frame}{Structured payments contract}
%\vspace{-.1in}
\begin{columns}
\begin{column}{.45\textwidth}
   \begin{itemize}
       \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity of payments.
       \vspace{.2in}
       \vfill \item Penalty fee not large < 1 USD on avg loan; $\approx$avg. transport cost to go to branch.
       \vspace{.2in}
       \vfill \item We view it as a way to increase salience of monthly payment.
    \end{itemize}
    \end{column}
\begin{column}{.45\textwidth}
    \vspace{-.3in}
        \begin{figure}[H]
            \includegraphics[width=0.78\textwidth]{Figuras/fc_contract.png}
        \end{figure}
    \end{column}
    \end{columns}
\end{frame}

@@

\vspace{-.1in}
\begin{itemize}
    \item Subjective value.
    \item Entire day's wage per visit + transport cost.
    \item Raw liquidity adjustment: as if she borrowed to pay us at 7\%  %~(removed $\sum_t P^{I}_{it}$)
\end{itemize}
%\vspace{-.4in}
\begin{table}[H]
\label{table_robustness_fc}
\begin{center}
\resizebox{0.85\textwidth}{!}{
\small{\input{Tables/fc_robustnessESB}}
}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{fc\_robustness.do}
\end{table}
   % \hyperlink{main_results}{\beamerbutton{Back}}
\end{frame}

@@

\begin{frame}{Identification afforded by experiment}
Our 3-arm experiment + exclusion restriction allows us to estimate: 
\begin {itemize}
 \item Treatment on the Treated (ToT).
 \item Treatment on the Untreated (TuT).
\end{itemize}
\vspace{.1in}
Notation: 
\begin{itemize}
    \item Potential outcomes $(Y_0,Y_1,C)$, where $C$ is borrower's ``choice-type'' $\in\{0,1\}$, i.e. $\{SQ,Structure\}$
    \item Assignment: $Z \in \{0,1,2\}$, i.e. $\{SQ,Structure,Choice\}$.  
    \item Treatment: $D \in \{0,1\} $, i.e. $\{SQ,Structure\}$.
\end{itemize}
\vspace{.1in}
Assumptions:
\begin{itemize}
    \item $Z \perp (Y_0,Y_1,C)$, achieved by randomization
    \item $D = \mathbbm{1}(Z_i \neq 2) Z + \mathbbm{1}(Z_i=2) C$.
\end{itemize}
\end{frame}

\begin{frame}{ToT and TuT are identified}
Exclusion restrictions (for a given person $i$):
\begin{itemize}
        \item No warm-glow 
        (NWG) from choosing: $Y_i(d=1,z=2)=Y_i(d=1,z=1) \equiv Y_{i1}$
        \item  No warm-glow from not choosing: $Y_i(d=0,z=2)=Y_i(d=0,z=0) \equiv Y_{i0}$
    \end{itemize}
\pause \vfill This allows us to write the effect for borrower $i$ as:
\begin{center}
    $Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right]$
\end{center}

@@

\pause Prop:
\begin{itemize}
    \item ToT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} $
     \item TuT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1-\mathbbm{E}(D_i|Z_i=2)} $
     %\item Also identified: 
     %\begin{itemize}
      %   \item Average Selection on Gains $ASG:=ToT-TuT$
         %\item Average Seletion Bias $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$
         %\item Average Selection on Levels $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$
     %\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{If structure works, why don't people choose it?}
\begin{itemize}
    \item \textbf{1. Learning?} one possibility is that they would eventually demand it as they try it.
    \begin{itemize}
        \item One problem is that lenders may not provide it.
    \end{itemize}
    \vfill \item  Test those assigned to Structure or Status quo return and have a choice (i.e. get choice arm).
        \begin{itemize}
        \item Problems: small sample and returning is endogenous.
    \end{itemize}
 \end{itemize}  
 \vspace{.1in}
\begin{table}[H]
\begin{center}
 \resizebox{0.65\textwidth}{!}{
\small{\input{Tables/learning_exp}}
}
\end{center}
\end{table}
 %\hyperlink{learning}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Can impatience explain it?}
    \begin{itemize}
    \item  Structured payments imposes up-front costs for later benefits (collateral recovery).  
    \item  Requires an interest rate > 4,000\% to make NPV TuT =0. 
    \end{itemize}
\vspace{.1in}
\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect_tut.pdf}
    \end{center}
\end{figure}   
\end{frame}

@@

% \begin{frame}{Over confidence?}
%     \begin{itemize}
%     \item   Recall that at baseline, people were, on average, overconfident about recovering pawns.
%     \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which sub-populations have larger TuT.
% \vspace{.3in}
%     \begin{align*}
%         1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{TuT}\Pr(X_i=1 | C_i=0) \\
%         \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{TuT}\Pr(X_i=0 | C_i=0)
%     \end{align*}

% %and we will say that the variable $B_i$ explains the ToT whenever one of the terms (ratio weighted by the probability) is statistically significant from zero, (close to one), and the other term is statistically zero.
%     \end{itemize}
% \end{frame}

@@

\begin{itemize}
    \item   Recall that at baseline, people were, on average, overconfident about recovering pawns.
    \vfill \item We find that TuT>0 is concentrated on those that said they will recover with 100\% probability. 
    \begin{itemize}
        \item Conceptually, overconfidence could explain low take up and TuT>0.
    \end{itemize}
    %\vfill \item In contrast, we don't find this result for PB (as measured by us).
\end{itemize}
\begin{figure}[H]
        \includegraphics[width=0.5\textwidth]{Figuras/tut_beh_partition.pdf}
\end{figure}
\end{frame}

\begin{frame}{Determinants of Sure Confidence}
        % \begin{figure}
        % \caption{What attributes correlate with Sure Confidence?}
        % \centering
        % \includegraphics[width=0.65\textwidth]{Figuras/determinants_confidence_100.pdf}
        % \end{figure}

The Sure-Confident are:
\begin{itemize}
    \item   Older, more educated men who
    \item   Have savings and do not report financial stress or trouble meeting bills, and 
    \item   Are likely to be relied upon by family members.
\end{itemize}        
\end{frame}

\section{Targeting?}

@@

\begin{columns}
\begin{column}{.43\textwidth}
\begin{figure}    
\centering
\includegraphics[width=0.99\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
\end{figure}
\end{column}
\begin{column}{.5\textwidth}
   \begin{itemize}
     \item Assuming NWG conditional on X's, we use (Athey et.al. 2019) causal forests to estimate $E[Y_1 - Y_0| X = \mathbf{x}, C = 0]$, i.e. CTuT
     \vspace{.1in}
     \begin{itemize}
	 \item Causal forest partition X to produce the biggest difference in TE across leaves, and gives a ``personalized'' TE according to the leaf borrowers are assigned to.
    \end{itemize}
    \vspace{.2in}
    \item Only 7\% of borrowers's estimated CTuT < 0.
    \vspace{.2in}
    \item >1/2 lose at least 10pp APR from not choosing.
    \end{itemize}
\end{column}
\end{columns}
\end{frame}

% \begin{frame}{Example of a Causal Tree}
%     \begin{figure}
%         \centering
% \includegraphics[width=0.7\textwidth]{Figuras/crf_apr.pdf}
%         \end{figure}
% \end{frame}

% \begin{frame}{Fraction that forgo benefit:  Choice Arm}
%         \begin{figure}
%        % \label{choose_wrong}
%         %\caption{Mistakes in choice arm}
%         \centering
%         \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
%         \end{figure}
% \begin{itemize}
%     \item   Use Random Forest to estimate ToT, TuT conditional on covariates.
%     \item   Those making either choice make mistakes if benefit of other choice is higher.
%     \item $>$ 70\% of non-choosers would have seen some benefit from assignment to commitment.
%     \item  $<$ 20\% of choosers made a mistake.
% \end{itemize}        
% \end{frame}

% \begin{frame}{91\% better off being forced into Structure}
%         \begin{figure}
%         \centering
%         \includegraphics[width=0.65\textwidth]{Figuras/cdf_CATE.pdf}
%         \end{figure}
% \end{frame}

@@

>>>>

\date{April 2025}

@@

\begin{frame}{Flexibility and high default}
    \begin{itemize}
    \item Pawn loans are highly \textbf{flexible:} pay-when-you-want within 90 days, no structured payments, no reminders.
        \begin{itemize}
            \item This lack of structure contrasts with microfinance loans.
        \end{itemize}
    \vfill \item High default rates, 44\% in our data (an order of magnitude larger than microfinance).
    \begin{itemize}
        \item Subjective value higher than gold value $\Rightarrow$ inefficient to lose.
        \item Gold-buying stores (avg of 2.8) close to pawn shops (pay $\approx$ 100\% of its gold value).
    \end{itemize}
     \item \vfill \textbf{Optimistic borrowers}: In our data, borrowers are very optimistic about recovery: avg. subjective probability of recovery (0-100) in our data is 92\%, and 72\% say recovery is certain.
     \begin{itemize}
         \item Conditional on default: more than 2/5 pay towards recovery (avg. 42\% loan value).
     \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Questions}
     \begin{enumerate}
         \item  Could borrowers benefit from \textbf{structured} (frequent) payments, but contract not be offered by lenders?
         \item \vfill If such a contract were offered, would it be demanded by borrowers?
        \item \vfill Would \textbf{mandating} frequent payments reduce financing costs more than giving a menu of \textbf{choices}?
        \item \vfill What is the treatment effect of structured payments on those who would \textbf{not} choose them (TuT)? 
        \begin{itemize}
            \item Are non choosers leaving money on the table?
        \end{itemize} 
     \end{enumerate}
\end{frame}

\begin{frame}{Outline}
     \large   
     \begin{itemize}
        \item \textbf{Context: Borrowers, contracts, data, outcomes}
         \item \vfill ``Mandates-Choice'' Experimental Design
         \vfill\item Main results
          \vfill\item Exploiting ``Mandates-Choice'' Design: ToT, TuT
         \vfill\item Why low demand (mostly speculative)
         %\vfill \item Targeting?
     \end{itemize}
\end{frame}

@@

\begin{frame}{Mandates-Choice Design}
\label{treatment_arms}
   \begin{itemize}
    \vfill \item Randomization at the branch-day level.  Analysis at the pawn level.
    \begin{enumerate}
        \vfill \item Status quo contract (Control, 1770 obs)
       \vfill \item Structured payments (Frequent payments, 1954 obs)
       \vfill \item Choice between the two (2580 obs)
    \end{enumerate}
       \vfill \item  This design enables us to explore whether giving Choice saves borrowers more money than assigning them to a Structured payment contract or Status-quo.
       \vfill \item The existence of a Choice arm allows us to measure if there is demand for such a contract. Will also allow more cool stuff... 
\end{itemize}
\end{frame}

\begin{frame}{More details on implementation}
    \begin{itemize}
        \item Randomization built into IT system
        \item No person knew sequence of days-contract type.
        \item  Personnel were told that consecutive same contract-type could occur, and that randomization was happening in many branches.
        \item We had materials to explain the contract in simple terms.
        \item Borrowers explained back the contract.
        \item Appraisers no incentive either way (paid flat wage). Enumerators were there every day all day.
        \item Virtually no borrower left the branch without pawning.
        \item They seem to like this lender: 87\% pawned there before.
        \item Stick to branch: we cannot find experimental subjects in 2 different experimental branches. 
    \end{itemize}
\end{frame}

\begin{frame}{Standard (status quo) contract}
\vspace{-.2in}
    \begin{figure}[H]
    \label{ExplanatoryMaterial1}
    \begin{center}
        \includegraphics[width=0.34\textwidth]{Figuras/sq_contract.png}
    \end{center}
\end{figure}
\end{frame}

\begin{frame}{Structured payments contract}
%\vspace{-.1in}
\begin{columns}
\begin{column}{.45\textwidth}
   \begin{itemize}
       \vfill \item New contract identical to the status quo contract, except that it enhances the regularity of payments.
       \vspace{.2in}
       \vfill \item Penalty fee not large < 1 USD on avg loan; $\approx$avg. transport cost to go to branch.
       \vspace{.2in}
       \vfill \item We view it as a way to increase salience of monthly payment.
    \end{itemize}
    \end{column}
\begin{column}{.45\textwidth}
    \vspace{-.3in}
        \begin{figure}[H]
            \includegraphics[width=0.78\textwidth]{Figuras/fc_contract.png}
        \end{figure}
    \end{column}
    \end{columns}
\end{frame}

@@

\vspace{-.1in}
\begin{itemize}
    \item Subjective value.
    \item Entire day's wage per visit + transport cost.
    \item Raw liquidity adjustment: as if she borrowed at 7\% to pay us.  %~(removed $\sum_t P^{I}_{it}$)
\end{itemize}
%\vspace{-.4in}
\begin{table}[H]
\label{table_robustness_fc}
\begin{center}
\resizebox{0.85\textwidth}{!}{
\small{\input{Tables/fc_robustnessESB}}
}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{fc\_robustness.do}
\end{table}
   % \hyperlink{main_results}{\beamerbutton{Back}}
\end{frame}

@@

\begin{frame}{Identification afforded by experiment}
Our 3-arm experiment + exclusion restriction allows us to estimate: 
\begin {itemize}
 \item Treatment on the Treated (ToT).
 \item Treatment on the Untreated (TuT).
\end{itemize}
\vspace{.1in}
Notation: 
\begin{itemize}
    \item Potential outcomes $(Y_0,Y_1,C)$, where $C$ is borrower's ``choice-type'' $\in\{0,1\}$, i.e. $\{SQ,Structure\}$
    \item Assignment: $Z \in \{0,1,2\}$, i.e. $\{SQ,Structure,Choice\}$.  
    \item Treatment: $D \in \{0,1\} $, i.e. $\{SQ,Structure\}$.
\end{itemize}
\vspace{.1in}
Assumptions:
\begin{itemize}
     \item $Z \perp (Y_0,Y_1,C)$, achieved by randomization.
    \item $D = I(Z_i \neq 2) Z + I(Z_i=2) C$.
\end{itemize}
\end{frame}

\begin{frame}{ToT and TuT are identified}
Exclusion restrictions (for a given person $i$):
\begin{itemize}
        \item No agency effect 
        (NAE) from choosing: $Y_i(d=1,z=2)=Y_i(d=1,z=1) \equiv Y_{i1}$
        \item  No agency effect from not choosing: $Y_i(d=0,z=2)=Y_i(d=0,z=0) \equiv Y_{i0}$
    \end{itemize}
\pause \vfill This allows us to write the outcome for borrower $i$ as:
\begin{center}
    $Y_i = I(Z_i =0) Y_{i0} + I(Z_i = 1)  Y_{i1}  + I(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right]$
\end{center}

@@

\pause Prop:
\begin{itemize}
    \item ToT := $E(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{E(Y_i|Z_i=2) - E(Y_i|Z_i =0)}{E(D_i|Z_i=2)} $
     \item TuT := $E(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{E(Y_i|Z_i=1) - E(Y_i|Z_i =2)}{1-E(D_i|Z_i=2)} $
     %\item Also identified: 
     %\begin{itemize}
      %   \item Average Selection on Gains $ASG:=ToT-TuT$
         %\item Average Seletion Bias $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$
         %\item Average Selection on Levels $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$
     %\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{If structure works, why don't people choose it?}
\begin{itemize}
    \item \textbf{1. Learning?} one possibility is that they would eventually demand it as they try it.
    \begin{itemize}
        \item One problem is that lenders may not provide it.
        \item (Experience pawning \textit{negatively} correlated with take up of structure).
    \end{itemize}
    \vfill \item  Test those assigned to Structure or Status quo return and have a choice (i.e. get choice arm).
        \begin{itemize}
        \item Problems: small sample and returning is endogenous.
    \end{itemize}
 \end{itemize}  
 \vspace{.1in}
\begin{table}[H]
\begin{center}
 \resizebox{0.65\textwidth}{!}{
\small{\input{Tables/learning_exp}}
}
\end{center}
\end{table}
 %\hyperlink{learning}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Can impatience explain it?}
    \begin{itemize}
    \item  Structured payments imposes up-front costs for later benefits (collateral recovery).  
    \item  Requires annual discounting > 4,000\% to make NPV TuT =0. 
    \end{itemize}
\vspace{.1in}
\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect_tut.pdf}
    \end{center}
\end{figure}   
\end{frame}

@@

@@

\begin{itemize}
    \item   Recall that at baseline, people were, on average, overconfident about recovering pawns.
    \vfill \item We find that TuT>0 is concentrated on those (28\%) that said they will recover with 100\% probability. 
    \begin{itemize}
        \item Conceptually, overconfidence could explain low take up and TuT>0.
        \item Intuitively: overconfidents underappreciate the benefit of structure.
    \end{itemize}
    %\vfill \item In contrast, we don't find this result for PB (as measured by us).
\end{itemize}
\begin{figure}[H]
        \includegraphics[width=0.5\textwidth]{Figuras/tut_beh_partition.pdf}
\end{figure}
\end{frame}

\begin{frame}{Sure confidence and Present bias}
        % \begin{figure}
        % \caption{What attributes correlate with Sure Confidence?}
        % \centering
        % \includegraphics[width=0.65\textwidth]{Figuras/determinants_confidence_100.pdf}
        % \end{figure}
Do we need to model overconfidence and PB?
\begin{itemize}
    \item We can think of borrower overconfidence of recovery arising from a belief that their distribution of future income is shifted to the right vis-a-vis the real one.
    \item It can also come from PB naivete itself, as those types will spend more than expected and have less money to pay.
\end{itemize}
\vfill Determinants of Sure Confidence. The Sure-Confident are:
\begin{itemize}
    \item   Older, more educated men who
    \item   Have savings and do not report financial stress or trouble meeting bills, and 
    \item   Are likely to be relied upon by family members.
\end{itemize}

\begin{comment}

\begin{frame}{Do we need to model overconfidence and PB? (sketch)}

\begin{itemize}
    \item We can think of borrower overconfidence of recovery arising from a belief that their distribution of future income is shifted to the right vis-a-vis the real one.
    \begin{itemize}
        \item It can also come from PB naivete itself, as those types will spend more than expected and have less money to pay.
    \end{itemize}
   \pause \vfill  \item Simple model features PB and overconfidence, 3 periods: 
\begin{itemize}
        \item Period 3 (default): Pay iff: $u\bigl(y_3 - R \cdot \mathit{\text{Outstanding  debt}}\bigr) + v 
\;>\; u(y_3)$.   
  \item Period 2: Pay interim $\kappa$ iff \[
u(y_2 - k)
\;+\;
\beta\,\delta 
\;\mathbb{E}_{y_3|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R(L - k)\bigr) + v,\;u(y_3)\bigr\}\Bigr]
\quad\]
\[>\quad
u(y_2)
\;+\;
\beta\,\delta
\;\mathbb{E}_{y_3|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R\,L\bigr) + v,\;u(y_3)\bigr\}\Bigr].
\]
        %\item Period 2: Get stochastic income $y_2$. In Structure contract pay $\kappa$; no payment required in SQ contract.
        \item Period 1: Decide on contract $\in$ \{SQ,Structure\} to Max discounted expected utility. 
    \end{itemize}
    \vfill\item We plan to have income follow a distribution $f(y;\mu)$, and overconfidents think $\hat{\mu}>\mu$. Model PB in the standard ($\beta,\delta$) way. 
    \pause \vfill\item Parameters: [L,R,$\kappa$,\delta$,$\beta$,$\hat{\beta},$\nu$,$\mu$]; Decisions: [$t_1$:(SQ or S), $t_2$:(pay $\kappa$ or not), $t_3$:(default and lose $\nu$)].
    \vfill\item Show that both PB naivete and OC can explain TUT>0 in the model.
\end{itemize}

\end{comment}

\begin{comment}

% =======================
% Period T=3: Default vs. Repay
% =======================
\subsection{Period 3}
\[
\text{Repay if and only if}\quad
u\bigl(y_3 - R \cdot \mathit{\text{Outstanding  debt}}\bigr) + v 
\;>\;
u(y_3).
\]
\[
\text{Otherwise, default.}
\]
\[\text{Outstanding debt} =\begin{cases}
  L-k &\text{if pay in T=2}\\
  L &\text{if not pay in T=2}
\end{cases}\]

% =======================
% Period T=2: Pay k vs. Not Pay k
% =======================
\subsection{Period 2}
\[
u(y_2 - k)
\;+\;
\beta\,\delta 
\;\mathbb{E}_{y_3|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R(L - k)\bigr) + v,\;u(y_3)\bigr\}\Bigr]
\quad\]
\[>\quad
u(y_2)
\;+\;
\beta\,\delta
\;\mathbb{E}_{y_3|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R\,L\bigr) + v,\;u(y_3)\bigr\}\Bigr].
\]
\[
\text{If the left side is greater, pay } k; \text{ otherwise, do not pay } k.
\]
\vspace{5mm}

For overconfident people:
\[
u(y_2 - k)
\;+\;
\beta\,\delta 
\;\mathbb{E}_{y_3'|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R(L - k)\bigr) + v,\;u(y_3)\bigr\}\Bigr]
\quad>\quad
u(y_2)
\;+\;
\beta\,\delta
\;\mathbb{E}_{y_3'|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R\,L\bigr) + v,\;u(y_3)\bigr\}\Bigr].
\]

% =======================
% Period T=1: Commitment vs. No Commitment
% =======================
\subsection{Period 1}
\[
\underbrace{
\beta\,\delta\,\mathbb{E}_{y_2|y_1}[\,u(y_2)\,] 
\;+\;
\beta\,\delta^2
\,\mathbb{E}_{y_3|y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R\,L\bigr)+v,\;u(y_3)\bigr\}\Bigr]
}_{\text{No-Prepayment}}
\quad\]

\[<\quad
\underbrace{
\beta\,\delta\,\mathbb{E}_{y_2|y_1}[\,u(y_2 - k)\,]
\;+\;
\beta\,\delta^2
\,\mathbb{E}_{y_3|y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R(L-k)\bigr)+v,\;u(y_3)\bigr\}\Bigr]
}_{\text{Prepayment}}.
\]
\[
\text{Choose commitment if the right side is greater.}
\]
\end{comment}

@@

\begin{columns}
\begin{column}{.43\textwidth}
\begin{figure}    
\centering
\includegraphics[width=0.99\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
\end{figure}
\end{column}
\begin{column}{.5\textwidth}
   \begin{itemize}
     \item Assuming NAE conditional on X's, we use (Athey et.al. 2019) causal forests to estimate $E[Y_1 - Y_0| X = \mathbf{x}, C = 0]$, i.e. CTuT
     \vspace{.1in}
     \begin{itemize}
	 \item Causal forest partition X to produce the biggest difference in TE across leaves, and gives a ``personalized'' TE according to the leaf borrowers are assigned to.
    \end{itemize}
    \vspace{.2in}
    \item Only 7\% of borrowers's estimated CTuT < 0.
    \vspace{.2in}
    \item >1/2 lose at least 10pp APR from not choosing.
    \end{itemize}
\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{Contributions to Literature}

\begin{itemize}
    \item  Few studies of pawn lending.
    \vfill \item Mandates-vs-choice Design is new to the literature. Simultaneously identify both TOT, TUT, ASG without the need for auxiliary structural modeling assumptions. Fowlie et al (2021), Karlan and Zinman (2009), Beaman et al (2023) do not identify TUT effects. 
    \vfill \item Relatively small literature selection-on-gains and paternalism (e.g. Laibson 2018). Walters (2018): distance-based instrument with structural model, finds students who select into more effective schools have smaller treatment effects. Saddoff et al (2019) shows that individuals with the most time-inconsistent preferences in food choice are the least likely to demand commitment. 
    \vfill \item Contract design: Pande and Field (2008) find no effects from frequent repayment schemes. Field et al (2013), Barboni et al (2023) find productive benefit of flexibility in microfinance.
    \vfill \item Large literature on demand for commitment.  We separately point-identify and estimate the effects of commitment for borrowers who would and would not choose it. 
\end{itemize}
